Equipo 7

### 2021-05-08 final/script.Rmd
Update script.Rmd

#ccreo el data final (por mientras)

data<-as.data.frame(merge(censos,planeas_del_10_al_19, by= c("INEGI"))) %>% 
       na.omit()  %>% mutate(cambio_internet=internet_20-internet_10,
                             cambio_pc=pc_20-pc_10,
                             cambio_esp= top_50_esp_19-top_50_esp_10,
                             cambio_mat= top_50_mat_19-top_50_mat_10)

>>>>

#creo el data final (por mientras)

data<-as.data.frame(merge(censos,planeas_del_10_al_19, by= c("INEGI"))) %>% 
       na.omit()  %>% mutate(cambio_internet=internet_20-internet_10,
                             cambio_pc=pc_20-pc_10,
                             cambio_esp_bottom=esp_1_19-esp_1_10,
                             cambio_esp_top=esp_IV_19-esp_IV_10,
                             cambio_mat_bottom=mat_1_19-mat_1_10,
                             cambio_mat_top=mat_IV_19-mat_IV_10)
